Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-05-23 paper/meg_exps.tex
supmat

The raw data was then segmented 100ms before word onset and 1.000 sec after
word onset. Time $t=0$ms corresponds to the word onset. Finally, each resulting
segment was baseline-corrected between -100ms and 0ms, and decimated by 5 and
thus led a sampling frequency of 240Hz. Figure \ref{fig:megavg} shows
the average response of the magnetometers evoked by the words presented to the
first subject.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{We plot the coefficients corresponding to each of the features,
  describing their importance over time after stimuli onsets. We can observe that visual features start peaking around 150ms, while lexical features peak around 400ms. We show a similar plot for the Ridge regression baseline (forward) in Figure \ref{fig:ridgebaselineresult}.}
  \label{fig:megresult}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/ridgecv_baseline_result.pdf}
  \caption{Regression baseline. Coefficients appear to be
  linearly correlated, unlike our method Fig. \ref{fig:megresult}.}
  \label{fig:ridgebaselineresult}
\end{figure}

>>>>

The raw data was then segmented 100ms before word onset and 1.000 sec after
word onset. Time $t=0$ms corresponds to the word onset. Finally, each resulting
segment was baseline-corrected between -100ms and 0ms, and decimated by 5 and
thus led a sampling frequency of 240Hz. Figure 1 in the supplementary material
shows the average response of the magnetometers evoked by the words presented
to the first subject.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{We plot the coefficients corresponding to each of the features,
  describing their importance over time after stimuli onsets. We can observe that visual features start peaking around 150ms, while lexical features peak around 400ms. We show a similar plot for the Ridge regression baseline (forward) in the supplementary material.}
  \label{fig:megresult}
\end{figure}
